---
title: "DataScience Learning"
author: "Kalidoss"
date: "April 2, 2017"
output: html_document
---

# Data Visualization using R ggplot

Loading the packages required which has the some dataset we can use for visualization

```{r}
#install.packages("tidyverse")
library(tidyverse)


```

Now, Just view the data in table format

```{r}
mpg

summary(mpg)

str(mpg)

```

Let's start with simple scatter plot
```{r}
ggplot(mpg, aes(x=displ, hwy) ) +
  geom_point()
```

This plot shows that it has some negative correlation of mileage with respect to Engine size

```{r}
ggplot(mpg ) +
  geom_point( aes(x=displ, y=hwy, color=class ))
```

Let us visualze in other way using size aesthetic instead of color
```{r}
ggplot(mpg ) +
  geom_point( aes(x=displ, y=hwy, size=class ))
```

Other way of visualizing the plot such as alpha and shape

```{r}
ggplot(mpg ) +
  geom_point( aes(x=displ, y=hwy, alpha=class ))
ggplot(mpg ) +
  geom_point( aes(x=displ, y=hwy, shape=class ))
```

Visualize the plot using Facets, Using this we can include additional varaible into the plot particularly categorical variables

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~class, nrow=2)
```

Facet plotting on the combination of two variables

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ cyl)
```
Not to facet on rows or column, use . instead of variable name as below

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
## Using Geometric Objects in ggplot

```{r}
ggplot(data=mpg) +
  geom_smooth(aes(x=displ, y=hwy))
```


Adding categorical varaible  (drv) in this plot, This categorical variable says that 
 * 'f' - front-wheel drive
 * 'r' - rear wheel drive
 * '4' - four wheel drive

```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype=drv ))
```

Same plot can be achieved using aesthetic parma 'group' instead of 'linetype'. But 'group' will not add Legend to the plot

```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, group=drv ))
```

Using Multiple geom object to the plot to create more meaning full visualization. 

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy )) + 
  geom_smooth() +
  geom_point()
```

